Joint maximum-likelihood of phylogenies and ancestral states is not consistent

### 2018-07-11 joint_inf.tex
fix table ref

We provide a full description of our optimization procedure in the Appendix, but briefly, we perform 81 maximizations for each separate likelihood function in Table~\ref{table:}.
For each function, we optimize the objective starting at five separate initial values to mitigate problems with small curvature of the objective surface and nonconcavity.
We compute these maxima over a lattice in steps of $10^{-2}$ for $x^*$ and $y^*$ from $0$ to $1$.
Our optimization code can be found at \url{https://github.com/matsengrp/joint-inf/}.

>>>>

We provide a full description of our optimization procedure in the Appendix, but briefly, we perform 81 maximizations for each separate likelihood function in Table~\ref{tab:likelihoods}.
For each function, we optimize the objective starting at five separate initial values to mitigate problems with small curvature of the objective surface and nonconcavity.
We compute these maxima over a lattice in steps of $10^{-2}$ for $x^*$ and $y^*$ from $0$ to $1$.
Our optimization code can be found at \url{https://github.com/matsengrp/joint-inf/}.
